---
title: "regresion"
author: "Cristian S치ez Mardones"
date: "18-01-2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Regresi칩n lineal costos medicos

***

[Data set original](https://www.kaggle.com/mirichoi0218/insurance)

Columns

* age: age of primary beneficiary

* sex: insurance contractor gender, female, male

* bmi: Body mass index, providing an understanding of body, weights that are relatively high or low relative to height,
objective index of body weight (kg / m ^ 2) using the ratio of height to weight, ideally 18.5 to 24.9

* children: Number of children covered by health insurance / Number of dependents

* smoker: Smoking

* region: the beneficiary's residential area in the US, northeast, southeast, southwest, northwest.

* charges: Individual medical costs billed by health insurance

***

* Diremos que el modelo es aceptable si explica sobre un 85% de los datos

* Diremos que el modelo es bueno si explica sobre un 90% de los datos

Cargamos los datos

```{r}
df = read.csv('insurance.csv')
head(df)
dim(df)

train <- df[c(1:1150), ]
test <- df[c(1151:dim(df)[1]), ]
```

Gr치fica de la predicci칩n de edad vs precio

```{r}
plot(train$age, train$charges, col='dodgerblue')
abline(lm(charges~age, data=train), col="orangered")
summary(lm(charges~age, data=train))$r.squared
```

Agregamos el bmi

```{r}
plot(train$age, train$charges, col='dodgerblue')
abline(lm(charges~age+bmi, data=train), col="orangered")
summary(lm(charges~age+bmi, data=train))$r.squared
```

Buscamos el mejor modelo

```{r}
summary(lm(charges~age+bmi+region, data=train))$r.squared
summary(lm(charges~age+bmi+region+smoker, data=train))$r.squared
summary(lm(charges~age+bmi+region+smoker+sex, data=train))$r.squared
summary(lm(charges~age+bmi+region+smoker+sex+children, data=train))$r.squared
```

Nos quedamos con el modelo que incluye todas las variables

```{r}
model <- lm(charges~age+bmi+region+smoker+sex+children, data=train)
prediction_y <- predict(model, test)
correlacion <- cor(test$charges, prediction_y)
```

El modelo explica los datos en un `r round(correlacion*100, 2)`% los datos, con lo que podemos afirmar que nuestro modelo es aceptable.








